---
title: "Assignment 4"
author: "Mohamed Megahed"
date: "4/18/2020"
output:
  word_document: default
  html_document: default
---

### Predict the type of a breast tumor (benign or malignant). 
**The data is loaded using the mlbench library, data(BreastCancer)**
A data frame with 699 observations on 11 variables, one being a character variable, 9 being ordered or nominal, and 1 target class.

```{r}
library(caret)
```

```{r setup, include=FALSE}
library(mlbench)
data("BreastCancer")
```

*** Understanding Data structure
```{r}
summary(BreastCancer)
levels(BreastCancer$Class)
```

** checking if there any missing data
```{r}
# Check if there are any missing values:
anyNA(BreastCancer)
sum(is.na(BreastCancer))
```
** we have 16 missing values in our dataset.
### Cleaning missing and excluding the ID variable
```{r}
B_Cancer <- na.omit(BreastCancer)[,c(2:11)]
```

```{r}
set.seed(123)
intrain <- createDataPartition(y = B_Cancer$Class, p= 0.7, list = FALSE)
train_data <- B_Cancer[intrain,]
test_data <- B_Cancer[-intrain,]
```

```{r}
set.seed(123)
svm.model<-train(Class~.,data=train_data,method='svmLinear', scale = FALSE)
svm.model
```

### Examining cost values (1,2.5,6.25) and Predicting the test data
```{r}
set.seed(123)
Grid_Serach <- expand.grid(.C=c(1,2.5,6.25))
#Building a support vector machine model
svm_Grid<-train(Class~.,
                 data=train_data,
                 method='svmLinear',
                 tuneGrid=Grid_Serach,
                 scale = FALSE)
svm_Grid

preds_svm_test <- predict(svm_Grid, test_data[1:9])  # predicting with the new SVM model        
table(pred = preds_svm_test, true = test_data$Class)

plot(svm_Grid)
```

***After examining the (1,2.5,6.25) values of cost it is clear that when Cost is equal 1 it has the best accuracy which is 94.47%***